% Jason R. Blevins - Curriculum Vitae
%
% Copyright (C) 2004-2015 Jason R. Blevins <jrblevin@sdf.org>
% http://jblevins.org/
%
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely.  No attribution is
% required in any resulting documents.  I do ask that you please leave
% this notice and the above URL in the source code if you choose to
% redistribute this file.

%\documentclass[10pt,letterpaper]{article}
\documentclass[margin]{res}

\textwidth=5.2in 
%\resumewidth=5pt
\sectionskip=25pt
\newsectionwidth{200pt}

%    \usepackage{sectsty}

\renewcommand{\ttdefault}{\sfdefault{iwona}}
%\renewcommand{\normalfont}{\sfdefault}

\renewcommand{\sectionfont}{\large}
    
%\fontfamily{cmss}


%\usepackage{etoolbox}
%\patchcmd{\thebibliography}{\section*{\refname}}{}{}{}

%\usepackage{multibib}
%
%\newcites{pri,sec}{Publications,Publications in Preparation}

%\usepackage{geometry}
%\usepackage{enumitem}

% Fonts
%\usepackage[urw-garamond]{mathdesign}
%\usepackage[T1]{fontenc}
%\usepackage{fontspec}
%\setmainfont{Calibri}
%\usepackage{helvet}
%\setlength{\textwidth}{5.1in} % Text width of the document

% Set your name here
\def\Aname{Geoffrey Newman}

\usepackage{hyperref}
% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\Aname},
  pdfkeywords = {biomedical engineering, bme, bci, brain computer interface, neuroengineering, neural engineering},
  pdftitle = {\Aname: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

%\geometry{
%  body={6.5in, 9.0in},
%  left=1.0in,
%  top=1.0in
%}
%
%% Customize page headers
%\pagestyle{myheadings}
%\markright{\name}
%\thispagestyle{empty}

% Custom section fonts
%\usepackage{sectsty}
%\sectionfont{\rmfamily\mdseries\Large}
%\subsectionfont{\rmfamily\mdseries\itshape\large}

% Other possible font commands include:
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% Don't indent paragraphs.
%\setlength\parindent{0em}

%% Make lists without bullets and compact spacing
%\renewenvironment{itemize}{
%  \begin{list}{}{
%    \setlength{\leftmargin}{1.5em}
%    \setlength{\itemsep}{0.25em}
%    \setlength{\parskip}{0pt}
%    \setlength{\parsep}{0.25em}
%  }
%}{
%  \end{list}
%}
%\setlist[enumerate]{itemsep=0.25em}

  
\begin{document}

%
%% Place name at left
%{\huge \name}
%
%% Alternatively, print name centered and bold:
%%\centerline{\huge \bf \name}
%
%\bigskip
%
%\begin{minipage}[t]{0.495\textwidth}
%  Department of Biomedical Engineering \\
%  Johns Hopkins School of Medicine \\
%  720 Rutland Avenue, Ross 720 \\
%  Baltimore, MD 21205
%\end{minipage}
%\begin{minipage}[t]{0.495\textwidth}
%  Phone: (646) 344-0831 \\
%  Office: 101 Clark Hall \\
%  Email: \href{mailto:geoffrey@jhu.edu}{geoffrey@jhu.edu}
%\end{minipage}

\name{\Huge{Geof\*frey Newman}\\[12pt]}

\address{Department of Biomedical Engineering \\
  Johns Hopkins School of Medicine \\
  720 Rutland Avenue, Ross 720 \\
  Baltimore, MD 21205}
  
\address{Phone: (646) 344-0831 \\
  Office: 101 Clark Hall \\
  Email: \href{mailto:geoffrey.nemwan@gmail.com}{geoffrey.nemwan@gmail.com} \\
  Website: \href{http://geoffrey.webhop.me}{http://geoffrey.webhop.me}}
  

\begin{resume}

\bigskip
\rule{\resumewidth}{2mm}  % Horizontal line after name; adjust line thickness by changing the '1pt'

\section{\MakeUppercase{Education}}

\textbf{Ph.D. Biomedical Engineering}, Johns Hopkins University, Expected September 2015.
\begin{itemize}
    \item \emph{Dissertation:} ``Network Models of Neural Recordings''.
    \item \emph{Committee:} N. Thakor, N. Crone, E. Niebur.
\end{itemize}
\textbf{B.Eng. Biomedical Engineering}, \textit{Magna Cum Laude},
    City College of the City University of New York, 2008.
\begin{itemize}
	    \item \emph{Minor:} Applied Mathematics.
\end{itemize}
    
\rule{\linewidth}{1mm}  % Horizontal line after name; adjust line thickness by changing the '1pt'

\section{\MakeUppercase{Research Experience}}

\textbf{Research Assistant}--JHU. 
Brain Computer Interface, 
PI: Nitish Thakor, 2008--Present.
\begin{itemize}
	\item Employed graph theory and signal processing techniques to solve neuroscience problems.
	\item Utilized machine learning techniques to decode movement intent from neural recordings.
\end{itemize}

\textbf{Research Assistant}--CCNY. 
Eye Movement and Vision, 
PI: Jay Edelman, 2006--2008.
\begin{itemize}
	\item Investigated movement planning of saccades via eye tracking data and non-invasive neural recordings.
	\item Created a graphical user interface to simplify data preprocessing.
\end{itemize}
	 
\rule{\linewidth}{1mm}  % Horizontal line after name; adjust line thickness by changing the '1pt'
	
\section{\MakeUppercase{Publications}}

\textbf{Geoffrey Newman}, Matt Fifer, Heather Benz, Nathan Crone, and Nitish Thakor. Eigenvector centrality reveals the time course of task-specic electrode connectivity in human ECoG. In \textit{Neural Engineering (NER), 2015 7th International IEEE/EMBS Conference}. IEEE, In Publication.

Nitish Thakor, Matthew Fifer, Guy Hotson, Heather Benz, \textbf{Geoffrey Newman}, Griffin Milsap, and Nathan Crone. Neuroprosthetic limb control with electrocorticography: Approaches and challenges. In \textit{Engineering in Medicine and Biology Society (EMBC), 2014 36th Annual International Conference of the IEEE}, pages 5212--5215. IEEE, 2014.

\textbf{Geoffrey Newman}*, Vikram Aggarwal*, Marc Schieber, and Nitish Thakor. Identifying neuron communities during a reach and grasp task using an unsupervised clustering analysis. In \textit{Engineering in Medicine and Biology Society, EMBC, 2011 33rd Annual International Conference of the IEEE}, pages 6401--6404. IEEE, 2011.

Sarah Ying, \textbf{Geoffrey Newman}, Young-Seok Choi, Hyoung-Nam Kim, Alessandro Presacco, Mayuresh Kothare, and Nitish Thakor. Cerebellar ataxia patients are able to use motor imagery to modulate mu-band power in a pilot study of EEG-based brain-computer interface control. In \textit{Neural Engineering (NER), 2011 5th International IEEE/EMBS Conference}, pages 192--195. IEEE, 2011.

Rong Liu, \textbf{Geoffrey Newman}, Sarah Ying, and Nitish Thakor. Improved BCI performance with sequential hypothesis testing. In \textit{Engineering in Medicine and Biology Society, EMBC, 2011 33rd Annual International Conference of the IEEE}, pages 4215--4218. IEEE, 2011.

Simon Kelly, John Foxe, \textbf{Geoffrey Newman}, and Jay Edelman. Prepare for conflict: EEG correlates of the anticipation of target competition during overt and covert shifts of visual attention. \textit{European Journal of Neuroscience}, 31(9):1690--1700, 2010.

\textbf{Geoffrey Newman}, Sarah Ying, Young-Seok Choi, Hyong-Nam Kim, Alessandro Presacco, Mayuresh Kothare, and Nitish Thakor. Brain computer interface in cerebellar ataxia. In \textit{26th Southern Biomedical Engineering Conference SBEC 2010}, April 30-May 2, 2010, College Park, Maryland, USA, pages 289--292. Springer, 2010.

\rule{\linewidth}{1mm}  % Horizontal line after name; adjust line thickness by changing the '1pt'

\section{\MakeUppercase{Publications in Preparation}}

\textbf{Geoffrey Newman}, Matt Fifer, Nathan Crone, and Nitish Thakor. Graph theoretic analysis of human ECoG connectivity. \textit{Neuroimage}, In Preparation.

\textbf{Geoffrey Newman}*, Ryan Smith*, Nathan Crone, and Nitish Thakor. Detecting communities of motor and premotor neurons during a reach and grasp task. \textit{Frontiers in Computational Neuroscience}, In Preparation.

\textbf{Geoffrey Newman}, Nathan Crone, and Nitish Thakor. K-means cluster analysis of human ECoG high gamma power reveals distinct phases of neural processing. \textit{Neural Systems and Rehabilitation Engineering, IEEE Transactions on}, In Preparation.

\rule{\linewidth}{1mm}  % Horizontal line after name; adjust line thickness by changing the '1pt'

\section{\MakeUppercase{Awards \& Fellowships}}

NIH Neuroengineering Training Initiative Training Fellowship, 2008--2010.
National Institute of Biomedical Imaging and Bioengineering (NIBIB), National Institute of Health (NIH) Grant
T32EB003383.

Howard Hughes Undergraduate Research Award, City College of New York, 2008.

Whitaker Foundation Undergraduate Research Scholarship, City College of New York, 2004--2008.

Advanced Placement Scholar with Distinction, Bronx High School of Science, 2004.

\rule{\linewidth}{1mm}  % Horizontal line after name; adjust line thickness by changing the '1pt'
%\section{\MakeUppercase{Invited Seminar Presentations}
%
%Morris Meister Research Lecture, The Bronx High School of Science, 2009
%
%
%\moveleft\hoffset\vbox{\hrule width\textwidth height 1pt}\smallskip % Horizontal line after name; adjust line thickness by changing the '1pt'

%\section{\MakeUppercase{Conference Presentations}}
%
%41st Annual Society for Neuroscience Meeting (SfN), Washington DC, November 12, 2011.
%
%33rd Annual International Conference of the IEEE Engineering in Medicine and Biology Society (EMBC), Boston, MA, August 30, 2011.
%
%5th International Conference of the IEEE/EMBS Neural Engineering (NER), Cancun, Mexico, April 27, 2011.
%
%Training Grantees Meeting, National Institute of Biomedical Imaging and Bioengineering (NIBIB), Bethesda, MD, June 24, 2010.
%
%26th Southern Biomedical Engineering Conference (SBEC) 2010, College Park, MD, April 30, 2010. 
%
%\rule{\linewidth}{1mm}  % Horizontal line after name; adjust line thickness by changing the '1pt'

\section{\MakeUppercase{Professional Activities}}

\textbf{Assistant Managing Editor}, Medical and Biological Engineering and Computing, 2013--Present.

\textbf{Reviewer}, Medical and Biological Engineering and Computing, 2014--Present.

\textbf{Member}, Institute of Electrical and Electronics Engineers (IEEE).

\textbf{Member}, Society for Neuroscience (SfN).

\textbf{Member}, Tau Beta Pi Engineering Honors Society (TBP).

\rule{\linewidth}{1mm}  % Horizontal line after name; adjust line thickness by changing the '1pt'

\section{\MakeUppercase{Teaching Assistantship}}

System Bioengineering II (Neuroscience):
\begin{itemize}
	\item Led weekly recitation for 50 students.
\end{itemize}

Biomedical Instrumentation:
\begin{itemize}
	\item Assisted 10 groups of 4 students in circuit design and 
	debugging, in addition to Computer Aided Design.
\end{itemize}

\rule{\linewidth}{1mm}  % Horizontal line after name; adjust line thickness by changing the '1pt'

\section{\MakeUppercase{Miscellaneous}}

\textit{Programming Languages:} 
\begin{itemize}
\item Matlab, C++, Java, LaTeX, Python, Qt, HTML, SQL.
\end{itemize}

\textit{Computer Systems and Software:} 
\begin{itemize}
\item Linux, Cloud Computing (Digital Ocean: Droplets, Amazon: EC2, S3, Map Reduce), Photoshop/GIMP, Cadence VLSI design tool, PTC Creo, SolidWorks, AutoCAD.
\end{itemize}

\textit{Languages:} 
\begin{itemize}
\item Native in English, reading and basic speaking competence in Japanese.
\end{itemize}

%\rule{\linewidth}{1mm}  % Horizontal line after name; adjust line thickness by changing the '1pt'
% Footer
%\bigskip
%{\small Last updated: \today}

\end{resume}

\end{document}
